Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-28 paper-v1.tex
Alice and Bob (beginning) @naszam

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS's hashes are then stored inside the smart contracts' state that is timestamped in the Ethereum Blockchain where it remains unaltered and indelible. This notarization process is called Proof of Existence (PoE).
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach.

@@

\subsubsection{AntsReview}
AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
 1. To upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS} and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
 2. To specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
 3. To specify the amount of Ether for the reward that will be transferred from Alice to the contract.

Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by sepcifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.

>>>>

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach.

@@

\subsubsection{AntsReview.}
AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
 \newline 1. \emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
 \newline 2. \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
 \newline 3. \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
 \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
